Evaluation of probabilistic photometric redshift estimation approaches for \textsc{LSST}

### 2019-03-15 paper/main.tex
macros
worked through GPZ
shorter title
removing unused macro
adding back conclusion
code macros

% Custom commands from LSST DESC, see texmf/styles/lsstdesc_macros.sty
\usepackage{lsstdesc_macros}
% \usepackage{natbib}
% \usepackage{subcaption}
\usepackage[colorinlistoftodos]{todonotes}
% \usepackage[colorlinks=true, allcolors=blue]{hyperref}
\usepackage{multirow}
\usepackage{xspace}
\usepackage{enumitem}
\usepackage{graphicx}
\usepackage{wasysym}
\usepackage{amsmath}
\usepackage{amsfonts}
\graphicspath{{./}{./figures/}}
\bibliographystyle{mnras}%mn2e

@@

% can easily change these to specify posterior throughout, etc
\newcommand{\pz}{photo-$z$}
\newcommand{\pzpdf}{\pz\ PDF}
\newcommand{\Pz}{Photo-$z$}
\newcommand{\Pzpdf}{\Pz\ PDF}
\newcommand{\nz}{$N(z)$}

@@

\title{Evaluating approaches to deriving photometric redshift posterior probability distribution functions for \textsc{LSST}}

@@

%\input{./tex/conclusion}

@@

In addition to packages cited in the text, analyses performed in this paper used the following software packages: \textsc{Numpy} and \textsc{Scipy} \citep{numpyscipy}, \textsc{Matplotlib} \citep{matplotlib}, \textsc{Seaborn} \citep{seaborn}, \textsc{minFunc} \citep{minfunc}, \textsc{pySkyNet} \citep{pyskynet}, and {\textsc photUtils} from the \lsst\ simulations package \citep{lsstphotutils}.

@@

% This work used some telescope which is operated/funded by some agency or consortium or foundation ...

% The DESC acknowledges ongoing support from the Institut National de Physique Nucleaire et de Physique des Particules in France; the Science \& Technology Facilities Council in the United Kingdom; and the Department of Energy, the National Science Foundation, and the LSST Corporation in the United States.
%
% DESC uses resources of the IN2P3 Computing Center (CC-IN2P3--Lyon/Villeurbanne - France) funded by the Centre National de la Recherche Scientifique; the National Energy Research Scientific Computing Center, a DOE Office of Science User Facility supported by the Office of Science of the U.S. Department of Energy under Contract No. DE-AC02-05CH11231; STFC DiRAC HPC Facilities, funded by UK BIS National E-infrastructure capital grants; and the UK particle physics grid, supported by the GridPP Collaboration.
%
% This work was performed in part under DOE Contract DE-AC02-76SF00515.

% We acknowledge the use of An-External-Tool-like-NED-or-ADS.

%{\it Facilities:} \facility{LSST}

@@

% Include both collaboration papers and external citations:
\bibliography{main,lsstdesc}

>>>>

% Custom commands from LSST DESC, see texmf/styles/lsstdesc_macros.sty
\usepackage{lsstdesc_macros}
% \usepackage{natbib}
% \usepackage{subcaption}
\usepackage[colorinlistoftodos]{todonotes}
% \usepackage[colorlinks=true, allcolors=blue]{hyperref}
\usepackage{multirow}
\usepackage{xspace}
\usepackage{enumitem}
\usepackage{graphicx}
\usepackage{wasysym}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{footmisc}
\graphicspath{{./}{./figures/}}
\bibliographystyle{mnras}%mn2e

@@

% can easily change these to specify posterior throughout, etc
\newcommand{\pz}{photo-$z$}
\newcommand{\pzpdf}{\pz\ PDF}
\newcommand{\Pz}{Photo-$z$}
\newcommand{\Pzpdf}{\Pz\ PDF}
\newcommand{\chisq}{$\chi^{2}$}

@@

\title{Evaluation of probabilistic photometric redshift estimation approaches for \textsc{LSST}}

@@

\input{./tex/conclusion}

@@

In addition to packages cited in the text, analyses performed in this paper used the following software packages: \code{Numpy} and \code{Scipy} \citep{numpyscipy}, \code{Matplotlib} \citep{matplotlib}, \code{Seaborn} \citep{seaborn}, \code{minFunc} \citep{minfunc}, \code{pySkyNet} \citep{pyskynet}, and \code{photUtils} from the \lsst\ simulations package \citep{lsstphotutils}.

@@

@@

\bibliography{main,lsstdesc}
